---
date: "`r Sys.Date()`"
output: 
  rmarkdown::pdf_document
params: 
  title:
    label: "Report title:"
    value: "Akalura Salmon Escapement Report"
    input: text
  author:
    label: "Author:"
    value: Kevin Van Hatten
    input: text
  email:
    label: "Email:"
    value: kevin_vanhatten@fws.gov
    input: text
  phone:
    label: "Phone number:"
    value: 907-539-1669
    input: text
  input_data:
    label: "Input dataset (csv):"
    value:
    input: file
---

---
title: `r params$title`
author: `r params$author`
---

```{r setup, include=FALSE, cache=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```


<!-- param$name -->
<!-- param$email -->
<!-- param$phone -->

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dat <- import_format(params$input_data)
models <- model_escapement(dat)
boots <- boot_escapement(dat, models)


#plot_hrly(dat, models)


```


```{r}
#boots <- boot_escapement(dat=dat, models=models)
```

### Project Description

### Results
I imported and formatted the raw dataset. I subsetted the raw dataset to only include observations when video data were available. I evaluated linear, polynomial linear, segmented, and segmented polynomial models to assess the relationship between video and photo counts (response = video). Using Delta AICc to evaluate the competing model set, I found the most parsimonious model to be the `r tolower(models$aic_table$Modnames[[1]])` model. Model diagnostics indicated normal residuals and constant error variance (homoskedasticity). 
```{r linear_model, echo=F, warning=F, fig.align="left", message=F}
# load("../output/models/mod_best.Rdata")
# 
# library(knitr)
# library(xtable)
# library(tidyverse)
# 
# mod.best %>%
#   summary() %>%
#   xtable() %>%
#   kable(caption="Summary of the most parsimonious model (the linear model)")
```


```{r}
```

Using the top model, I calculated the estimated daily salmon passage, total annual escapement, and daily salmon passage. I calculated bootstrapped 95% CIs to estimate uncertainty around the annual escapement estimate. 
  
```{r plot_boot, echo=F, fig.cap="Mean minimum escapement estimates for Akalura River, Kodiak Island, Alaska. Error bars represent 95% CIs"}

p.boots <- plot_boot_escapement(boots)
p.boots[["min_escape"]]
```


```{r boot summart tbl, echo=FALSE}
kable::kable(boots$summary)
```


\newpage

## R Session Information
```{r session_info, echo=FALSE, results='asis'}
sessionInfo()
```

