---
title: "Salmon Escapement Estimate for Akalara River, Kodiak Refuge"
date: "`r Sys.Date()`"
output: 
  rmarkdown::pdf_document
params: 
  name:
    label: "Your name:"
    value: Kevin Van Hatten
    input: text
  email:
    label: "Email address:"
    value: kevin_vanhatten@fws.gov
    input: text
  phone:
    label: "Phone number:"
    value: 907-539-1669
    input: text
  input_data:
    label: "Input dataset (csv):"
    value:
    input: file
---

---
author: `r params$name`
---

```{r setup, include=FALSE, cache=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```


<!-- param$name -->
<!-- param$email -->
<!-- param$phone -->

```{r, echo=FALSE, }
source("../../R/global.R")
source("../../R/import_format.R")
dat <- import_format(params$input_data)

source("../../R/analysis.R")
models <- model_escapement(dat)

source("../../R/plot.R")
p <- plot_hrly(dat, models)
p

```

### Project Description

### Results
I imported and formatted the raw dataset. I subsetted the raw dataset to only include observations when video data were available (data/derived/datud.Rdata).I evaluated linear, polynomial linear, segmented, and segmented polynomial models to assess the relationship between video and photo counts (response=video). Using Delta AICc to evaluate the competing model set, I found the most parsimonous model to be the linear model. Model diagnostics indicated normal residuals and constant error variance (homoskedasticity). 
```{r linear_model, echo=F, warning=F, fig.align="left", message=F}
# load("../output/models/mod_best.Rdata")
# 
# library(knitr)
# library(xtable)
# library(tidyverse)
# 
# mod.best %>%
#   summary() %>%
#   xtable() %>%
#   kable(caption="Summary of the most parsimonious model (the linear model)")
```


```{r}
```

Using the top model, I calculated the estimated daily salmon passage, total annual escapement, and daily salmon passage. I calculated bootstrapped 95% CIs to estimate uncertainty around the annual escapement estimate. 
  
```{r plot_boot, echo=F, fig.cap="Mean minimum escapement estimates for Akalura River, Kodiak Island, Alaska. Error bars represent 95% CIs"}
# load("../output/tables/results.Rdata")
# 
# ggplot(results, aes(x = as.factor(year), y = escapement)) +
#   geom_errorbar(data=results, aes(ymin = lower_ci, ymax = upper_ci),
#                 width = .1) +
#   geom_point() +
#   labs(x="Year", y = "Est. min. escapement")
```

\newpage  

<!-- ## Code -->
<!-- ```{r, code=readLines("../code/akalura.R"), eval=FALSE} -->
<!-- ``` -->

\newpage

## R Session Information
```{r session_info, echo=FALSE, results='asis'}
sessionInfo()
```

